### 2025-03-06 paper-aadm.tex
Copy paper to new template

% \documentclass[14pt]{mmcs-article}
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage{amsmath, amsthm, amsfonts, amssymb}

@@

%%%%% TODO

% Литература

% Разобрать комментарии по тексту

% Проверить буквы: чтобы не пересекались и что выбрали удачные

% Журнал: дискретная математика, шпрингер

% Abstract 250 слов

@@

@@

\section{Literature.}

% Список литературы: ~15 штук
% Брать ссылки из цитат
% Все цитаты привести к правильному виду

\begin{thebibliography}{0}

@@

%https://homepages.math.uic.edu/~pless/preprint/allerton.pdf

%% https://errorcorrectionzoo.org/

%% Discard

% 13

% Слишком общо, но можно по ссылкам пройтись
% \bibitem{quantum_error_correction}
% G. Zémor, “On Cayley Graphs, Surface Codes, and the Limits of Homological Coding for Quantum Error Correction”
% https://www.researchgate.net/publication/220776025_On_Cayley_Graphs_Surface_Codes_and_the_Limits_of_Homological_Coding_for_Quantum_Error_Correction

% \bibitem{metagraphs_and_applications}
% A. Basu, R.W. Blanning. Mategraphs and Their Applications
% ~-- %https://books.google.rs/books?id=9DlhUIJklqUC&printsec=frontcover#v=onepage&q&f=false

\end{thebibliography}

>>>>

% Use this file as a template for your text. Updated 18/03/2022.
% You may use your \newcommands placed in the marked space below
% Do not use separate files with macros

% Before processing this file, please make sure that the file
% aadmbook.cls is in the same folder with this file.
% The file aadmbook.cls can be downloaded from http://pefmath.etf.rs/aadmbook.cls

\documentclass[leqno]{aadmbook}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float} %package for figure and table placement 
%all necessary packages should be here

@@

@@

\pagestyle{myheadings}

\textwidth 28cc

\markboth{{\small\rm \hfill O.V. Arutyunov, V.A. Skorokhodov - header
\hfill}\hspace{-\textwidth}%
\underline{${{}_{}}_{}$\hspace{\textwidth}}}
{\underline{${{}_{}}_{}$\hspace{\textwidth}}\hspace{-\textwidth}%
{\small\rm \hfill Metagraph approach for construction of an (m, n)-regular bipartite graph with a given girth -header
\hfill}}

\setcounter{page}{1}
%\hoffset=-2.0em
\textheight 42cc

\parskip .5mm

\parindent 2cc

\begin{document}

% Your \newcommands below (if there are any):

\oddsidemargin 16.5mm
\evensidemargin 16.5mm

\thispagestyle{plain}

\begin{center}
{\large \sc  Applicable Analysis and Discrete Mathematics}

{\small available online at  http:/$\!$/pefmath.etf.rs }
\end{center}

\noindent{\small{\sc  Appl. Anal. Discrete Math.\ }{\bf x} (xxxx),xxx--xxx.}\\
\noindent{\scriptsize https://doi.org/10.2298/AADMxxxxxxxx}     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{5cc}
\begin{center}

{\large\bf  METAGRAPH APPROACH FOR CONSTRUCTION OF AN (M, N)-REGULAR BIPARTITE GRAPH WITH A GIVEN GIRTH
\rule{0mm}{6mm}\renewcommand{\thefootnote}{}%Enter at least one, but not more than 3 MSCs.
% First entered MSC will be a primary one, others (at most 2) will be secondary.
\footnotetext{\scriptsize ${}^{\ast}$Corresponding author. John Doe}
\footnotetext{\scriptsize 2020 Mathematics Subject Classification. FILL SUBJECT MSCs HERE.

\rule{2.4mm}{0mm}Keywords and Phrases. Fill Keywords and Phrases Here - at most 5, separated by commas.}}

\vspace{1cc}
{\large\it Oleg Arutyunov, Vladimir Skorokhodov}

\vspace{1cc}
\parbox{24cc}{{\small

Short abstract here (not more than 7 lines of text)

%Avoid citations in the  abstract, but if they are necessary, do not use labels from the
%main body of the article. For example, instead of  writing "formula (2)" , you
%should reproduce formula (2), or describe it in words. Instead of writing
%"the result  obtained in [1]" , you should write "the result obtained in
%{\sc J. A. Baker:}  {\it Isometries in normed spaces,}
%Amer. Math. Monthly {\bf 78} (1971), 655--658".

}}
\end{center}

% The paper should have at least two sections

%TODO: Сделать секции как в шаблоне

% \vspace{1.5cc}
% \begin{section}
% {FILL SECTION TITLE HERE}
% \end{section}

@@

\begin{table}[H]
\caption{This is a table caption. Tabels should be placed in the main text
near to the first time they are cited. Table caption should be above
the the table.}

\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
type & A & B\tabularnewline
\hline 
\hline 
expression & $\frac{a}{b}$ & $a+b$\tabularnewline
\hline 
expression & $a\cdot b$ & $\int f\left(x\right){\rm d}x$\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{thebibliography}{1}

%TODO: Proper references

%Fill the list of references in the alphabetical order here.
% Adopt the style like:

% \bibitem{bib1}
% {\small {\sc J. A. Baker:} {\it Isometries in normed spaces.}
% Amer. Math. Monthly, {\bf 78} (1971), 655--658.}

% \bibitem{bib2}
%  {\small {\sc A. Marshall, I. Olkin: }{\it Inequalities$:$ Theory of
% Majorization and Its Applications.} Academic Press, New York, 1979.}
% \end{thebibliography}

% \vspace{1cc}

% %Fill author(s) affiliation(s), address(es) and emails here:
% %example is shown
% \noindent
% {\bf John Doe}\\
% Department of Mathematics,\\
% University of Belgrade,\\
% Belgrade, Serbia\\
% E-mail: {\it joe.doe@mail.com}

% \vspace{0.1cc}

% \noindent
% {\bf Jane Doe}\\
% Department of Mathematics,\\
% University of Belgrade,\\
% Belgrade, Serbia\\
% E-mail: {\it jane.doe@mail.com}

@@
